Gammapy: A Python package for gamma-ray astronomy

### 2022-08-08 src/ms-review.tex
Update src/ms-review.tex
Co-authored-by: Bruno KHÉLIFI <khelifi@in2p3.fr>

The \code{SkyModel} object represents factorised model that combines the spectral,
spatial and temporal model components (by default the spatial and temporal components are
optional). SkyModel objects represents additive emission components, usually
sources or diffuse emission, although a single source can also be modeled by
multiple components. To handle list of multiple \code{SkyModel} objects, \gammapy
has a \code{Models} class.

@@

\subsection{gammapy.stats}
\label{ssec:gammapy-stats}
The \code{gammapy.stats} subpackage contains the fit statistics and associated
statistical estimators that are commonly used in \gammaray astronomy. In
general, \gammaray observations count Poisson-distributed events at various sky
positions, and contain both signal and background events. Estimation of the
number of signal events is done through likelihood maximization. In \gammapy,
the fit statistics are Poisson log-likelihood functions normalized like
chi-squares, i.e., they follow the expression $2 \time\cdot \log{\mathcal{L}}$,
where $\mathcal{L}$ is
the likelihood function used. The statistic function used when the expected
number of background events is known is the \emph{Cash} statistic
~\citep{Cash}. It is used by datasets using background templates such as the
\code{MapDataset}. When the number of background events is unknown and an off
measurement where only background events are expected is used, the statistic
function is WStat. It is a profile log-likelihood statistic where background
counts are marginalized parameters. It is used by datasets containing off
counts measurements such as the \code{SpectrumDatasetOnOff}, used for classical
spectral analysis.

>>>>

The \code{SkyModel} object represents factorised model that combines the spectral,
spatial and temporal model components (by default the spatial and temporal components are
optional). \code{SkyModel} objects represents additive emission components, usually
sources or diffuse emission, although a single source can also be modeled by
multiple components. To handle list of multiple \code{SkyModel} objects, \gammapy
has a \code{Models} class.

@@

\subsection{gammapy.stats}
\label{ssec:gammapy-stats}
The \code{gammapy.stats} subpackage contains the fit statistics and associated
statistical estimators that are commonly used in \gammaray astronomy. In
general, \gammaray observations count Poisson-distributed events at various sky
positions, and contain both signal and background events. Estimation of the
number of signal events is done through likelihood maximization. In \gammapy,
the fit statistics are Poisson log-likelihood functions normalized like
chi-squares, i.e., they follow the expression $2 \time\cdot \log{\mathcal{L}}$,
where $\mathcal{L}$ is
the likelihood function used. When the expected number of background events is known, the used statistic function 
 is the \emph{Cash} statistic
~\citep{Cash}. It is used by datasets using background templates such as the
\code{MapDataset}. When the number of background events is unknown and an off
measurement where only background events are expected is used, the statistic
function is WStat. It is a profile log-likelihood statistic where background
counts are marginalized parameters. It is used by datasets containing off
counts measurements such as the \code{SpectrumDatasetOnOff}, used for classical
spectral analysis.
